---
params: 
  title: ""
  publication_date: ""
  doi: ""
output: 
  html_document:
    anchor_sections: false
    theme: null
    highlight: null
    mathjax: null
    css: ["style.css", "https://fonts.googleapis.com/css?family=Source+Sans+Pro:400,700&display=swap"]
    self_contained: true
title: "`r params$title`"
---

```{r general-setup, include=FALSE}
## This file contains the ENGLISH version of the data story

# Set general chunk options
knitr::opts_chunk$set(echo = FALSE, fig.showtext = TRUE, fig.retina = 3, 
                      fig.align = "center", warning = FALSE, message = FALSE)

# Install pacman package if needed
if (!require("pacman")) {
  install.packages("pacman")
  library(pacman)
}

# Install snf.datastory package if not available, otherwise load it
if (!require("snf.datastory")) {
  if (!require("devtools")) {
    install.packages("devtools")
    library(devtools)
  }
  install_github("snsf-data/snf.datastory")
  library(snf.datastory)
}

# Load packages
p_load(tidyverse,
       lubridate,
       scales, 
       conflicted, 
       jsonlite,
       here, 
       ggiraph,
       readxl)

# Conflict preferences
conflict_prefer("filter", "dplyr")
conflict_prefer("get_datastory_theme", "snf.datastory")
conflict_prefer("get_datastory_scheme", "snf.datastory")

# Increase showtext package font resolution
showtext_opts(dpi = 320)

# Set the locale for date formatting (Windows)
Sys.setlocale("LC_TIME", "English")

# Create function to print number with local language-specific format 
print_num <- function(x) snf.datastory::print_num(x, lang = "en")

# Knitr hook for local formatting of printed numbers
knitr::knit_hooks$set(
  inline <- function(x) {
    if (!is.numeric(x)) {
      x
    } else {
      print_num(x)
    }
  }
)
```

```{r print-header-infos, results='asis'}
# Add publication date to header
cat(format(as_datetime(params$publication_date), "%d.%m.%Y"))

# Register the Google font (same as Data Portal, is not loaded twice)
cat(paste0("<link href='https://fonts.googleapis.com/css?family=", 
           "Source+Sans+Pro:400,700&display=swap' rel='stylesheet'>"))
```

```{r story-specific-setup, include=FALSE}
# Set story-specific variables etc. here
rd_ch <- read_excel(here("data", "RD_financing_CH.xlsx"))
rd_conf <- read_excel(here("data", "RD_financing_confederation.xlsx"))
rd_internat <- read_excel(here("data", "RD_financing_international_GERD.xlsx"))
```


<!-- Short lead (2-3 sentences) in bold -->

__Every year, the SNSF receives around one billion francs from the federal government. In 2019, a total of 22.9 billion Swiss francs was available for research and development (R&D) in Switzerland. Our country ranks seventh in terms GDP share spent on R&D.__

The private sector contributed almost two-thirds of the total funds available in 2019. The share of public investment in R&D by the federal government and cantons amounted to 27 per cent, which is slightly below the European average (30 per cent in 2018). Another 6 per cent comes from abroad, and 2 per cent comes from other sources in Switzerland. 

In addition to financing 65 per cent of R&D in Switzerland, the private sector carries out a large proportion (68 per cent) of R&D projects in the country. The situation is different for the federal government, which finances more than a quarter of R&D but conducts only 1 per cent itself. Conversely, universities carry out 29 per cent of R&D projects but finance a very small proportion.

<div class="plot-box">

<div class="plot-title">Financial expenditure for R&D in Switzerland in 2019</div>

```{r plot-1, out.width="100%", fig.height=2.5}
# Get data ready
rd_ch <- rd_ch %>%
  mutate(freq = Value / sum(Value)) %>% 
  arrange(desc(freq)) %>% 
  mutate(order = row_number()) %>%
  # Now calculate where the segment has to start (and end) per category
  mutate(seg_start = map_dbl(order, function(x) {
    prev_dist <- filter(., order < x) %>%
      pull(freq) %>%
      sum(na.rm = TRUE)
    prev_dist
  }),
  seg_end = seg_start + freq)

# create the color palette
my_color_palette <-
  tibble(
    category = rd_ch$Source_en,
    color = c("#4159AC", "#406AF5", "#4DD898", "#93E8D4", "#EFC900")
  )


# Create the plot
p_rd_ch <- rd_ch %>%
  ggplot(aes(x = 1, y = freq,
             fill =  reorder(Source_en, -order),
             # Define tooltip text for ggiraph
             tooltip = paste0("<b>", Source_en, "</b>\n", 
                              print_num(round(Value, digits = 0)), " million francs",
                              "\n", print_num(round(freq * 100, digits = 1)), "%"))) +
  geom_col_interactive(color = "white", width = 0.55) +
  geom_text(aes(x = ifelse(freq < 0.15, 1.375, 1.475),
                y = ifelse(freq < 0.15, seg_start + 0.0078, seg_start),
                label = Source_en,
                angle = ifelse(freq < 0.15, 90, 0)),
            vjust = 1,
            hjust = 0,
            color = "#4d4d4d", family = "Source Sans Pro",
            size = 3, fontface = "plain") +
  coord_flip() +
  get_datastory_theme() +
  scale_fill_manual(
    values = setNames(my_color_palette$color,
                      my_color_palette$category),
    guide = FALSE) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0.005, 0.005),
                     labels = percent_format(accuracy = 1)) +
  scale_color_manual(
    guide = FALSE,
    values = setNames(my_color_palette$color,
                      my_color_palette$category)
  ) +
  labs(title = "", subtitle = "", x = NULL, y = NULL) +
  theme(axis.text.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(color = "#d3d3d3", size = 0.3)) +
  expand_limits(x = 2.5)
# p_rd_ch
# Create ggiraph object
girafe(ggobj = p_rd_ch, 
       height_svg = 2.5, 
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F75858;stroke:white;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))

```

<div class="caption">
Excl. financing flows to other countries. Source: FSO, data from 2019.
</div>
</div>

### The SNSF receives a quarter of federal research funding 

In 2019, the federal government allocated a total of 4.7 billion Swiss francs to Swiss research. This amount includes funding for international research programmes in which Switzerland participates. Almost a quarter of the federal government’s funding goes to the SNSF. Switzerland’s largest funding agency uses the money to support research projects at universities and other institutions based on a competitive selection procedure.

In 2014, the SNSF share increased briefly to 28 per cent. The SNSF used the additional funds for backup schemes necessitated by Switzerland’s temporary exclusion from the European Horizon 2020 Framework Programme for Research and Innovation. 


<div class="plot-box">

<div class="plot-title">Federal expenditure on R&D in 2019</div>


```{r plot-2, out.width="100%", fig.height=3.3}

rd_conf <- rd_conf %>%
  mutate(freq = value_2019 / sum(value_2019)) %>% 
  arrange(desc(freq)) %>% 
  mutate(order = row_number()) %>%
  # Now calculate where the segment has to start (and end) per category
  mutate(seg_start = map_dbl(order, function(x) {
    prev_dist <- filter(., order < x) %>%
      pull(freq) %>%
      sum(na.rm = TRUE)
    prev_dist
  }),
  seg_end = seg_start + freq)

color <- colorRampPalette(colors = c("#406AF5", "#FFFFFF"))(7)

my_color_palette <-
  tibble(
    category = rd_conf$Category_en,
    color = color[1:6]
  )


# Create the plot
p_rd_conf <- rd_conf %>%
  ggplot(aes(x = 1, y = freq,
             fill =  reorder(Category_en, -order),
             # Define tooltip text for ggiraph
             tooltip = paste0("<b>", Category_en, "</b>\n",
                              print_num(round(value_2019, digits = 0)), " million francs",
                              "\n", print_num(round(freq * 100, digits = 1)), "%"))
         ) +
  geom_col_interactive(color = "white", width = 0.55) +
  geom_text(aes(x = ifelse(freq < 0.15, 1.375, 1.475),
                y = ifelse(freq < 0.15, seg_start + 0.0078, seg_start),
                label = Category_en,
                angle = ifelse(freq < 0.15, 90, 0)),
            vjust = 1,
            hjust = 0,
            color = "#4d4d4d", family = "Source Sans Pro",
            size = 3, fontface = "plain") +
  coord_flip() +
  get_datastory_theme() +
  scale_fill_manual(
    values = setNames(my_color_palette$color,
                      my_color_palette$category),
    guide = FALSE) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0.005, 0.005),
                     labels = percent_format(accuracy = 1)) +
  scale_color_manual(
    guide = FALSE,
    values = setNames(my_color_palette$color,
                      my_color_palette$category)
  ) +
  labs(title = "", subtitle = "", x = NULL, y = NULL) +
  theme(axis.text.y = element_blank(),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(color = "#d3d3d3", size = 0.3)) +
  expand_limits(x = 3.3) 

# Create ggiraph object
girafe(ggobj = p_rd_conf, 
       height_svg = 3.3, 
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F75858;stroke:white;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))

```


<div class="caption">
Incl. financing flows to foreign countries. Source: FSO, data from 2019.
</div>
</div>

### Switzerland ranks seventh internationally

To compare financial R&D investment between different countries, the OECD calculates the percentage of the corresponding gross domestic expenditure with reference to gross domestic product (GDP). Switzerland invests 3.15 per cent of GDP in R&D. As a result, it ranks seventh in a comparison of 15 nations with the highest levels of expenditure. Israel and Korea invest most in research, proportionately. Neighbouring Germany and Austria also allocate a greater percentage of funds to R&D than Switzerland.  

<div class="plot-box">

<div class="plot-title">Gross domestic expenditure on R&D as a percentage of GDP</div>

```{r plot-3, out.width="100%", fig.height=4}

p_rd_internat <- rd_internat %>% 
  arrange(value_2019) %>%
  # convert the column to a factor, according to the order of appearance.
  mutate(Country_en = fct_inorder(Country_en),
        my_color = if_else(Country_de == "Schweiz", "#F75858", "#4159AC")) %>% 
  ggplot(aes(x = value_2019,
             y = Country_en,
             fill = my_color,
             tooltip = paste0("<b>", Country_en, "</b>\n", 
                              print_num(round(value_2019, digits = 2)), "%"
                            ))) +
  geom_col_interactive(color = "white") +
  scale_fill_identity() +
  scale_x_continuous(breaks = seq(0, 5, 0.5)) +
  get_datastory_theme(gridline_axis = "x")


# Create ggiraph object
girafe(ggobj = p_rd_internat,
       height_svg = 5,
       options = list(
         opts_toolbar(saveaspng = FALSE),
         opts_hover(css = "fill:#F75858;stroke:#F75858;"),
         opts_tooltip(
           css = get_ggiraph_tooltip_css(),
           opacity = 0.8,
           delay_mouseover = 0,
           delay_mouseout = 0
         )
       ))
```

<div class="caption">
Top 15 countries in terms of R&D expenditure plus EU and OECD. Source: OECD, MSTI database, data from 2019.
</div>
</div>

<div class="info-box">

### Data and methods

<p>All data provided by the 
<a target="_blank" href="https://www.bfs.admin.ch/bfs/en/home/statistics/education-science/technology.html">Federal Statistical Office</a>.</p>

</div>

Data, text and code of this data story are <a href="https://github.com/snsf-data/datastory_rd_financing" target="_blank">available on Github</a> and <a href="https://doi.org/10.46446/datastory.rd-financing" target="_blank">archived on Zenodo</a>.<br>DOI: 10.46446/datastory.rd-financing